Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation

### 2014-11-14 approach.tex
added back

\subsection{Rendering}
\label{sec:rendering}
We made rendering engine that uses color, texture and material information in
CAD models to generate realistic rendering to simulate the natural image
statistics. The example rendering is
in Fig. \ref{fig:rendering}.

@@

\subsection{Whitened Histograms of Orientations (WHO)}
\label{sec:who}
Our technique for rendering and training template detectors on-the-fly
is drawing from recent work. Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
\cite{Hariharan12}, which uses feature statistics from natural images to whiten HOG
templates, making them more discriminative. Whitening is a common signal
processing operation for decorrelating a set of random variables
\cite{Martinsson05, Belouchrani00}. By whitening features, we remove 2nd order
correlation between all features.

>>>>

\subsection{Rendering}
\label{sec:rendering}

We used a public rendering engine to create realistic rendering and
depth. We used CAD models that contain color, texture and material information such as
transparency and reflectance to make the rendering as much realistic
as possible to simulate the natural image statistics. The example rendering is
in Fig. \ref{fig:rendering}. We also extracted depth information as well while
rendering to use in the reconstruction.

We used a collection of CAD models to make exemplar renderings of CAD models and for viewpoints. The
CAD models are cached so that when we fine-tune 2D-3D matching, so it can be rendered instantaneously.
We made the renderings to change focal length and yaw, pitch, roll so that we can fine tune the matching
continuously.

@@

\subsection{Whitened Histograms of Orientations (WHO)}
\label{sec:who}
Our technique for rendering and training template detectors on-the-fly
is drawing from recent work. Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
\cite{Hariharan12}, which uses feature statistics from natural images to whiten HOG
templates, making them more discriminative. Whitening is a common signal
processing operation for decorrelating a set of random variables

\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
whitening the signal,
\begin{equation}
\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
\end{equation}
we remove 2nd order correlation between all features. Since collecting covariance matrix for every template shape
 is expensive, \cite{Hariharan12} proposed easy way to synthesize
covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
method to generate $\Sigma$.
